---
title: "Party Panel 18.1-pre1 Report"
author: "Greater Good (Gjalt-Jorn Peters)"
date: "`r format(Sys.time(), '%d %b %Y at %H:%M:%S');`"
output:
  html_document:
    toc: true
    #toc_float: true
    toc_depth: 5
    theme: united
    css: "B:\\Data\\research\\party panel\\partypanel-shared\\party panel reports.css"
---

Introduction
------------

Party Panel is a Dutch panel study where determinants and beliefs underlying health behaviors in the Dutch nightlife are mapped. The fourth wave started on [[[ADD]]] 2018 and explored behavior related to [[[ADD]]].

This document is the report of the first pre-study, where members of expert organisations had the opportunity to respond to a number of open questions about which exact behavior they thought should be targeted in PP18.1. Note that this overview is not exhaustive; we also discussed potential behaviors with Rutgers, a Dutch sexual health organisation planning to release a campaign in 2018, so that the information about determinants from this Party Panel wave could inform that campaign.

```{r echo=FALSE, warning=FALSE, message=FALSE }

### Set basic configuration variables
if (!exists('ppWave')) ppWave <- '18.1';
if (!exists('ppReport')) ppReport <- 'pre1';
if (!exists('basePath')) basePath <- 'B:/Data/research/party panel';
if (!exists('surveyid')) surveyid <- '883163';
if (!exists('regularVars')) regularVars <- c('suggestion',
                                             'justification',
                                             'recruitment');
if (!exists('loopVars')) loopVars <- c('extraQuestions_vraag',
                                       'extraQuestJustificat_vraag');
if (!exists('loopNr')) loopNr <- 10;
if (!exists('personalDataQuestions')) personalDataQuestions <- c('personalInfo_name',
                                                                 'personalInfo_role',
                                                                 'personalInfo_organisation',
                                                                 'personalInfo_email');

if (!exists('requiredQuestions')) requiredQuestions <- c('suggestion');

### Dataset filename and version variables
privateDataFileRegEx <- '.*_\\[PRIVATE-version].*\\.csv';
privateFileIdentificationString <- "PRIVATE-";
publicFileIdentificationString <- "PUBLIC-";
dataPath <- file.path(basePath,
                      paste0('partypanel-', ppWave),
                      'preparation',
                      ppReport,
                      'data');
publicDataFilename <- paste0('survey_', surveyid, '_R_data_file_[PUBLIC-version].csv');
scriptFilename <- paste0('survey_', surveyid, '_R_syntax_file.R');

require('pander', quietly=TRUE);
require('xtable', quietly=TRUE);

knitr::opts_chunk$set(echo=FALSE);
knitr::opts_chunk$set(cache=FALSE);
knitr::opts_chunk$set(comment=NA);

options(width = 160);
options(xtable.type = "html");
panderOptions('knitr.auto.asis', FALSE);
panderOptions('table.split.table', Inf);

### Check for required package
if (!require('userfriendlyscience')) {
  stop("You need to have the userfriendlyscience package installed!");
}

### Make object(s) for Party Panel data
if (!exists('ppDat')) ppDat <- list();
if (!(ppWave %in% names(ppDat))) ppDat[[ppWave]] <- list();
ppDat[[ppWave]][[ppReport]] <- list();

########################################################################
### Data anonymization
########################################################################
    
### Get a list of all data files in data directory
privateDataFiles <-
  list.files(dataPath,
             pattern=privateDataFileRegEx);

### For this version of the script, there should be exactly one datafile
if (length(privateDataFiles) > 1) {
  stop("Multiple datafiles found - this should be impossible and is ",
       "indicative of compromised data integrity. Inspect the data ",
       "files carefully!");
} else if (length(privateDataFiles) == 1) {

  ### Run locally so all variables are automatically destroyed
  local({
    
    ### Read data
    privateDat <-
      importLimeSurveyData(datafile = file.path(dataPath, privateDataFiles),
                           scriptfile = file.path(dataPath, scriptFilename));
    
    ### Anonymize: set all values for variables containing personal data to NA
    privateDat[, personalDataQuestions] <- NA;
    
    ### Save anonymized datafile as public
    write.csv(privateDat,
              file.path(dataPath,
                        sub(privateFileIdentificationString,
                            publicFileIdentificationString,
                            privateDataFiles,
                            fixed=TRUE)));
    
  });
  
}

########################################################################
### Data loading
########################################################################
    
### Read public data
ppDat[[ppWave]][[ppReport]]$raw <-
  importLimeSurveyData(datafile = file.path(dataPath, publicDataFilename),
                       scriptfile = file.path(dataPath, scriptFilename));
ppDat[[ppWave]][[ppReport]]$cln <-
  ppDat[[ppWave]][[ppReport]]$raw;

########################################################################
### Missing value processing
########################################################################

### Count missing values
if (length(requiredQuestions) > 1) {
  ppDat[[ppWave]][[ppReport]]$cln$missings <-
    rowSums(is.na(ppDat[[ppWave]][[ppReport]]$cln[, requiredQuestions]), na.rm=TRUE);
} else {
  ppDat[[ppWave]][[ppReport]]$cln$missings <-
    as.numeric(is.na(ppDat[[ppWave]][[ppReport]]$cln[, requiredQuestions]));
}

### Remove rows with missing values
ppDat[[ppWave]][[ppReport]]$cln <-
  ppDat[[ppWave]][[ppReport]]$cln[ppDat[[ppWave]][[ppReport]]$cln$missings == 0, ];

```

The raw dataset contained `r nrow(ppDat[[ppWave]][[ppReport]]$raw);` rows and `r ncol(ppDat[[ppWave]][[ppReport]]$raw);` columns. After removal of empty entries, `r nrow(ppDat[[ppWave]][[ppReport]]$cln);` rows and `r ncol(ppDat[[ppWave]][[ppReport]]$cln);` columns remained.

The full list of variablenames is `r vecTxt(names(ppDat[[ppWave]][[ppReport]]$cln));`.

```{r echo=FALSE, results="asis"}

getLabel <- function(dat, varName) {
  return(attr(dat, 'variable.labels')[names(dat) == varName]);
}

showAnswersPerParticipant <- function(dat, varName, secondVarName=NULL) {
  if (length(na.omit(dat[, varName]))) {
    if (is.null(secondVarName)) {
      cat0("### ", varName, "\n",
           getLabel(dat, varName),  "\n\n",
           paste0(paste0("* id. ", dat[nchar(dat[, varName]) > 0 &
                                         !is.na(dat[, varName]), 'id'],
                         ": ", dat[nchar(dat[, varName]) > 0 &
                                     !is.na(dat[, varName]), varName]),
                  collapse="\n"), "\n\n");
    } else {
      cat0("### ", varName, "\n",
           getLabel(dat, varName),  "\n\n",
           getLabel(dat, secondVarName),  "\n\n",
           paste0(paste0("* id. ", dat[nchar(dat[, varName]) > 0 &
                                         !is.na(dat[, varName]), 'id'],
                         ": ", dat[nchar(dat[, varName]) > 0 &
                                     !is.na(dat[, varName]), varName],
                         " **-- JUSTIFICATION --** ", dat[nchar(dat[, varName]) > 0 &
                                     !is.na(dat[, varName]), secondVarName]),
                  collapse="\n"), "\n\n");
    }
  } else {
    cat("###", varName, "\nThis variable has no data.\n\n");
  }
}

for (currentVar in regularVars) {
  showAnswersPerParticipant(ppDat[[ppWave]][[ppReport]]$cln, currentVar);
}

for (currentVar in 1:10) {
  showAnswersPerParticipant(ppDat[[ppWave]][[ppReport]]$cln,
                            paste0(loopVars[1], currentVar),
                            paste0(loopVars[2], currentVar));
}

```


